### 2018-07-13 paper/sphinxes.tex
Sphinxes: fixes so that layers are constant-width

  \item \(r\) is the maximum number of nodes (\ie equivalent to the number of 
    layers) that a message will traverse before reaching its destination.

@@

We let \(w_L = \max_{N\in L}|N|\) be the maximum width of a layer, \ie the 
number of alternative nodes in the layer with the most alternative nodes.
We let \(w_H = 2w_L+1\) be the header width:
each layer must accommodate the layer nodes' ciphertexts and addresses, \ie  
\(2w_L\) elements of \(\kappa\) bits,
and the \ac{MAC}, \ie one element of \(\kappa\) bits.
(Note that we reveal the maximum number of alternatives per layer, but this is 
no different from ordinary \ac{OR} where there is a constant one node per 
layer.)

First we generate all the needed keys.
We compute \(\nu+1\) tuples
\begin{align*}
  \alpha_0 &\gets g^\sk,
  & \secret_0 &\gets \bin^\kappa,
  & \blind_0 &\gets \hash_\blind(\alpha_0, \secret_0) \\
  \alpha_1 &\gets g^{\sk\blind_0},
  & \secret_1 &\gets \bin^\kappa,
  & \blind_1 &\gets \hash_\blind(\alpha_1, \secret_1) \\
  &\vdots &&\vdots && \vdots \\
  \alpha_\nu &\gets g^{\sk \blind_0\dotsb \blind_{\nu-1}},
  & \secret_\nu &\gets \bin^\kappa,
  & \blind_\nu &\gets \hash_\blind(\alpha_\nu, s_\nu).
\end{align*}
In addition, we compute
\begin{align*}
  \secret_0^{(0)} &\gets \pk_{n_0^{(0)}}^\sk,
  & \dotsc, &
  & \secret_0^{(|L_0|-1)} &\gets \pk_{n_0^{(|L_0|-1)}}^\sk \\
  \secret_1^{(0)} &\gets \pk_{n_1^{(0)}}^{\sk \blind_0},
  & \dotsc, &
  & \secret_1^{(|L_1|-1)} &\gets \pk_{n_1^{(|L_1|-1)}}^{\sk \blind_0} \\
  & \vdots &&& \vdots \\
  \secret_\nu^{(0)} &\gets \pk_{n_\nu^{(0)}}^{\sk \blind_0\dotsb 
    \blind_{\nu-1}},
  & \dotsc, &
  & \secret_\nu^{(|L_\nu|-1)} &\gets \pk_{n_\nu^{(|L_\nu|-1)}}^{\sk 
    \blind_0\dotsb \blind_{\nu-1}}.
\end{align*}
We note that a node \(n_i^{(j)}\) can compute \(s_i^{(j)}\) since \[
  s_i^{(j)} = \pk_{n_i^{(j)}}^{\sk \blind_0\dotsb \blind_{i-1}} = 
  \alpha_i^{\sk_{n_i^{(j)}}}.
\]
We then construct the ciphertexts
\begin{align*}
  C_0 &= \prp'\left(\hash_{\prp'}\left(s_0^{(0)}\right), s_0\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_0^{(|L_0|-1)}\right), s_0\right) \\
  C_1 &= \prp'\left(\hash_{\prp'}\left(s_1^{(0)}\right), s_1\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_1^{(|L_1|-1)}\right), s_1\right) \\
  & \vdots \\
  C_\nu &= \prp'\left(\hash_{\prp'}\left(s_\nu^{(0)}\right), s_\nu\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_\nu^{(|L_\nu|-1)}\right) 
    s_\nu\right).
\end{align*}
and pad them to equal length with uniformly random bits, \ie length \(w_L = 
  \max_{i\in \{0, \dotsc, \nu\}} |C_i|\), where \(|C_i|\) denotes the length in 
bits (each ciphertext is \(\kappa\) bits).
These computations are summarized in \cref{fig:SphinxesKeys}.
\commentDaniel{We can probably comment out the figure.}

@@

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\CreateHeader}{$I, L = \{L_i\}_i$}
      \State $w_L\gets \max_{L_i\in L} |L_i|$
      \Comment{Layer width}
      \State $w_H\gets (2w_L+1)$
      \Comment{Header width}
      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
      b_\nu)\gets \ComputeKeys[L, w_L]$
      \State $\phi_0, \dotsc, \phi_\nu\gets \ComputePadding[\{s_0, \dotsc, 
      s_\nu\}, w_H]$
      \State $\alpha \gets \alpha_\nu$
      \State $C\gets C_\nu$
      \State $\beta \gets
        \left\{\left\{L_\nu\concat
            I\concat
            0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
          \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
        \phi_\nu$
      \Comment{$\beta_\nu$}
      \State $\gamma \gets \mac(\hash_\mac(s_\nu), \beta)$
      \Comment{$\gamma_\nu$}
      \For{$\nu-1\leq i\leq 0$}
          \State $\beta_i \gets \{L_{i+1}, \concat \gamma_{i+1}\concat 
          (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
          \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
      \EndFor
      \State \Return $(\alpha, C, \beta, \gamma), \{s_0, \dotsc, s_\nu\}$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:CreateHeader}%
    \dots
      $I\in \bin^\kappa$ is an identifier.
      $L = \{L_0, \dotsc, L_\nu\}$ such that $L_i, L_j\subset \N$, $L_i\cap L_j 
      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
      $L_\nu$ is the destination.
  }
\end{figure}

>>>>

  \item \(r\) is the maximum number of layers (hops, nodes) that a message will 
    traverse before reaching its destination.
    Further, let \(w_L\) be the maximum width of a layer, \ie the maximum 
    number of alternative nodes on a layer.

@@

Remember that \(w_L\) is the maximum width of a layer, \ie the number of 
alternative nodes in the layer.
We let \(w_H = 2w_L+1\) be the header width:
each layer must accommodate the layer nodes' ciphertexts and addresses, \ie  
\(2w_L\) elements of \(\kappa\) bits,
and the \ac{MAC}, \ie one element of \(\kappa\) bits.

First we generate all the needed keys.
We compute \(\nu+1\) tuples
\begin{align*}
  \alpha_0 &\gets g^\sk,
  & \secret_0 &\gets \bin^\kappa,
  & \blind_0 &\gets \hash_\blind(\alpha_0, \secret_0) \\
  \alpha_1 &\gets g^{\sk\blind_0},
  & \secret_1 &\gets \bin^\kappa,
  & \blind_1 &\gets \hash_\blind(\alpha_1, \secret_1) \\
  &\vdots &&\vdots && \vdots \\
  \alpha_\nu &\gets g^{\sk \blind_0\dotsb \blind_{\nu-1}},
  & \secret_\nu &\gets \bin^\kappa,
  & \blind_\nu &\gets \hash_\blind(\alpha_\nu, s_\nu).
\end{align*}
In addition, we compute
\begin{align*}
  \secret_0^{(0)} &\gets \pk_{n_0^{(0)}}^\sk,
  & \dotsc, &
  & \secret_0^{(|L_0|-1)} &\gets \pk_{n_0^{(|L_0|-1)}}^\sk \\
  \secret_1^{(0)} &\gets \pk_{n_1^{(0)}}^{\sk \blind_0},
  & \dotsc, &
  & \secret_1^{(|L_1|-1)} &\gets \pk_{n_1^{(|L_1|-1)}}^{\sk \blind_0} \\
  & \vdots &&& \vdots \\
  \secret_\nu^{(0)} &\gets \pk_{n_\nu^{(0)}}^{\sk \blind_0\dotsb 
    \blind_{\nu-1}},
  & \dotsc, &
  & \secret_\nu^{(|L_\nu|-1)} &\gets \pk_{n_\nu^{(|L_\nu|-1)}}^{\sk 
    \blind_0\dotsb \blind_{\nu-1}}.
\end{align*}
We note that a node \(n_i^{(j)}\) can compute \(s_i^{(j)}\) since \[
  s_i^{(j)} = \pk_{n_i^{(j)}}^{\sk \blind_0\dotsb \blind_{i-1}} = 
  \alpha_i^{\sk_{n_i^{(j)}}}.
\]
We then construct the ciphertexts
\begin{align*}
  C_0 &= \prp'\left(\hash_{\prp'}\left(s_0^{(0)}\right), s_0\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_0^{(|L_0|-1)}\right), s_0\right) \\
  C_1 &= \prp'\left(\hash_{\prp'}\left(s_1^{(0)}\right), s_1\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_1^{(|L_1|-1)}\right), s_1\right) \\
  & \vdots \\
  C_\nu &= \prp'\left(\hash_{\prp'}\left(s_\nu^{(0)}\right), s_\nu\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_\nu^{(|L_\nu|-1)}\right) 
    s_\nu\right).
\end{align*}
and pad them to \(w_L\kappa\) bits with uniformly random bits.
These computations are summarized in \cref{fig:SphinxesKeys}.
\commentDaniel{We can probably comment out the figure.}

@@

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\CreateHeader}{$I, L = \{L_i\}_i, w_L$}
      \State $w_H\gets (2w_L+1)$
      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
      b_\nu)\gets \ComputeKeys[L, w_L]$
      \State $\phi_0, \dotsc, \phi_\nu\gets \ComputePadding[\{s_0, \dotsc, 
      s_\nu\}, w_H]$
      \State $\alpha \gets \alpha_\nu$
      \State $C\gets C_\nu$
      \State $\beta \gets
        \left\{\left\{L_\nu\concat
            I\concat
            0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
          \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
        \phi_\nu$
      \Comment{$\beta_\nu$}
      \State $\gamma \gets \mac(\hash_\mac(s_\nu), \beta)$
      \Comment{$\gamma_\nu$}
      \For{$\nu-1\leq i\leq 0$}
          \State $\beta_i \gets \{L_{i+1}, \concat \gamma_{i+1}\concat 
          (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
          \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
      \EndFor
      \State \Return $(\alpha, C, \beta, \gamma), \{s_0, \dotsc, s_\nu\}$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:CreateHeader}%
    \dots
      $I\in \bin^\kappa$ is an identifier.
      $L = \{L_0, \dotsc, L_\nu\}$ such that $L_i, L_j\subset \N$, $L_i\cap L_j 
      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
      $L_\nu$ is the destination.
  }
\end{figure}
